---
title: "Penguins"
author: "Maria Dermit"
date: "28/07/2020"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
  knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE, echo=TRUE, 
                        dpi = 100, fig.width = 13,fig.height = 8)
library(tidyverse)
library(tidytuesdayR)
library(ggstatsplot)
library(here)
library(tidybayes)
library(GGally)
  

```

```{r}


## Getting the data
tuesdata <- tidytuesdayR::tt_load('2020-07-28')
tuesdata <- tidytuesdayR::tt_load(2020, week = 31)
penguins <- tuesdata$penguins
penguins %>% View()
```



## Exploring the data
penguins %>% group_by(species,sex) %>% 
 summarise(mean = mean(body_mass_g), n = n())
```{r}

penguins %>%
split(.$species) %>%
 map(~ lm(body_mass_g ~ sex, data = .x))
 
#Rename the sex parameter to called "NA" as "binary"
penguins<-penguins %>%  mutate_if(is.character,as.factor)  %>% 
mutate(sex = case_when(
sex=="female" ~ "female",
sex=="male" ~ "male",
 TRUE ~ "binary",
))
# plot
ggstatsplot::grouped_ggbetweenstats(
  data = penguins,
  x = sex,    
  xlab="",
  y = body_mass_g,
  grouping.var = species, # grouping variable
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  p.adjust.method = "bonferroni", # method for adjusting p-values for multiple comparisons
  # adding new components to `ggstatsplot` default
  ggplot.component = list(ggplot2::scale_y_continuous(sec.axis = ggplot2::dup_axis())),
  k = 3,
  title.prefix = "Species",
  palette = "default_jama",
  package = "ggsci",
  plotgrid.args = list(nrow = 3),
)

#ggsave("/Documents/TidyTuesdays/tidyversewebninar/20200728/plots/grouped_ggbetweenstats.jpg")

```

```{r}
penguins_clean = penguins %>%
  mutate(species = factor(species))
  
penguins_clean %>% 
  select(species,bill_length_mm,bill_depth_mm, flipper_length_mm    ,body_mass_g) %>% ggpairs(mapping = aes(color=species))
  
penguins_clean %>% 
 select(sex,species,bill_length_mm,bill_depth_mm, flipper_length_mm ,body_mass_g) %>% 
  ggplot(aes(species, body_mass_g, color = species)) +
  geom_boxplot(outlier.colour = NA) +
  geom_jitter(aes(alpha = sex), width = 0.15) +
  facet_wrap(~sex) 
```
Gentoo male penguins are the the chubbiest among these three species. 
It looks like more body weight is associated with longer flipper length and with less bill depth (so more pointy mouth).Lets do a linear regression model for body weigths of these cute penguins.


# Modeling 
```{r}
line_fit <- lm(body_mass_g~flipper_length_mm, data=penguins_clean)
line_smry <- summary(line_fit)
line_smry 
```
The R^2 value for this model is 0.759, which means that this model explains 75.9% of the variance (not sufficient).
We gain some information from our hypothesis test using this model.


We can use step function to choose a the model with lowest AIC.
```{r}
step_fit=step(lm(data=penguins_clean, body_mass_g ~ .),trace=0,steps=10000)
step_smry <- summary(step_fit)
step_smry 

best_fit <-lm(formula = body_mass_g ~ species + bill_length_mm + bill_depth_mm + 
    flipper_length_mm + sex + year, data = penguins_clean)

best_smry <- summary(best_fit)
best_smry 

```
This model captures 87.64% of total variance in body weight. The p-value: < 2.2e-16
This looks like a more robust highly predictive model.
```{r}

library(broom)
glance(best_fit) %>%
select( sigma, logLik, AIC, BIC, df.residual) %>%
  kable()

```

```{r}
penguins_clean$best_fit <- stats::predict(best_fit, newdata=penguins_clean)
err <- stats::predict(best_fit, newdata=penguins_clean, se = TRUE)
pred.int <-predict(best_fit, newdata = penguins_clean, interval = "confidence")
penguins_clean_conf <- cbind(penguins_clean, pred.int)

g <- ggplot(penguins_clean_conf)
g <- g + geom_point(aes(x=body_mass_g, y = best_fit), size = 2, colour = "blue")
g <- g + geom_smooth(data=penguins_clean_conf, aes(x=body_mass_g, y=best_fit, ymin=lwr, ymax=upr), size = 1.5, 
            colour = "red", se = TRUE, stat = "smooth") + 
  theme_classic()
  g
  
  anim <- g +
  transition_states(species,
                    transition_length = 2,
                    state_length = 1)

anim
```

